---
title: "My_Shiny_App"
author: "Nate Foulkes"
date: "11/21/2021"
output: ioslides_presentation
---
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE)
```

## My_Shiny_App

The purpose of this app is to allow a user to change some predictor values and see how their choices affect the Miles Per Gallon of a car.  
The prediction model takes advantage of the caret and parsnip packages in R. The model uses a Random Forest as a predictor algorithm.

## Why Have a Prediction App?   
MPG is important!  

- Gas Price Inflation 
- Owner Cost
- Environmental Impact
- Informed Purchasing Decisions
- Another Reason
- Yet Another Reason

## What Does the Dataset Look Like?   
Displayed is the first five rows of the mtcars dataset:

```{r cars, comment=""}
head(mtcars)
```

## Plot of MPG v. Displacement

```{r plot, warning=FALSE}
with(mtcars,plot(disp,mpg))
title(main = "MPG v. Displacement")
with(subset(mtcars, am == 1), points(disp,mpg, col= "blue"))
with(subset(mtcars, am == 0), points(disp,mpg, col= "red"))
legend("topright",pch=1,col=c("blue","red"), legend = c("Manual","Automatic"))
```

